Solutions to Integer Programming from Quantum Annealing

### 2020-05-10 paper/main.tex
minor words changed for dephasing

From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space. This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process. It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer. In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and become unaffected by decoherence. This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this. top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
\begin{align}
\label{eq:annealH}
 H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket. $L_j$ are the Lindblad operators for decoherence. $\{, \}$ denotes the anti-commutator. In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time. The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

>>>>

From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space. This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process. It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer. In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and {\color{blue}become unaffected by dephasing.} This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this. top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
\begin{align}
\label{eq:annealH}
 H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket. $L_j$ are the Lindblad operators for decoherence. $\{, \}$ denotes the anti-commutator. In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$. The amplitude damping model also includes the dephasing effect, where the dephasing time is fixed to $T_2=\frac{T_1}{2}$. For simplicity we assume all qubits having the same relaxation time. The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
